Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-31 paper.qmd
Update paper.qmd

As an example, we demonstrate a polyglot pipeline that simulates a Real Business
Cycle (RBC) model in [Julia]{.proglang}, trains an [XGBoost]{.pkg} forecasting
model in [Python]{.proglang} on the simulated data, visualises results in
[R]{.proglang}, and compiles a [Quarto]{.pkg} report. The code for this example
can be found in the [following
repository](https://github.com/b-rodrigues/rixpress_demos/tree/master/case-study)^[https://github.com/b-rodrigues/rixpress_demos/tree/master/case-study],
with additional details provided in the Appendix of this manuscript. Although
this example is purely synthetic and not of scientific significance, it
effectively demonstrates the capabilities of [rixpress]{.pkg}. It should also
be noted that the code [Julia]{.proglang}, [Python]{.proglang} and [R]{.proglang}
was generated by a large language model.

>>>>

As an example, we demonstrate a polyglot pipeline that simulates a Real Business
Cycle (RBC) model in [Julia]{.proglang}, trains an [XGBoost]{.pkg} forecasting
model in [Python]{.proglang} on the simulated data, visualises results in
[R]{.proglang}, and compiles a [Quarto]{.pkg} report. The code for this example
can be found in the [following
repository](https://github.com/b-rodrigues/rix_paper/tree/master/case-study)^[https://github.com/b-rodrigues/rix_paper/tree/master/case-study],
with additional details provided in the Appendix of this manuscript. Although
this example is purely synthetic and not of scientific significance, it
effectively demonstrates the capabilities of [rixpress]{.pkg}. It should also
be noted that the code [Julia]{.proglang}, [Python]{.proglang} and [R]{.proglang}
was generated by a large language model.
